On the Construction of a Collision-Free Schedule of Beacons in a Wireless Multi-Hop Network

### 2013-10-11 paper.tex
it turns out that things are really difficult unless the network agrees in a beginning and ending of the schedule

In order to solve this problem in a decentralized way, we need that the nodes keep trying different spots (or colours) until a solution is found.
%To be more specific, a node will pick the same color if none of its neighbours has picked that particular color.
Otherwise it will change the color.

@@

\subsection{The construction of a beacon schedule}

Each station picks a random spot in the schedule.
If it receives confirmation from all of its neighbors, it assumes that no collisions have occurred and keeps transmitting at that position.
This means that no other neighbor in the two-hop neighborhood has picked the same color.
In this case, the station will defer the transmission of the next beacon a deterministic number of spots equal to the schedule length $S$.

If a node in the two-node neighborhood pick the same color, the node that is a common neighbor of both will not receive the beacon and therefore will not confirm the correct reception.
In this case, the station will defer the transmission of the next beacon a random number of spots.
A sensible choice is to use an uniform variable between 1 and $2S$ so that the expectation of the random variable roughly coincides with the deterministic backoff used by successful stations.

>>>>

In order to solve this problem in a decentralized way, we need that the nodes keep trying different spots (or colours) until a solution is found.

@@

\subsection{The Construction of a Beacon Schedule}

When a station joins the networks it listens for a time $T_s$ to discover its neighbours.
After that it picks one the spots that seem to be empty: one that is not used in the two-hop neighbourhood.
When the joining station has transmitted one beacon, it has to listen to the $S-1$ spots and verify that all the neighbours acknowledge the beacon of the joining station.
If they do, the network is fine and joining station transmits again in the $S$-th slot.

Otherwise, it the beacon of the joining station is not acknowledged by one or more neighbours, the joining station will transmit in a random slot between $S$ and $2S-1$.
This patron keeps repeating as long as there are stations that don't see their beacon acknowledged.

%Each station picks a random spot in the schedule.
%If it receives confirmation from all of its neighbors, it assumes that no collisions have occurred and keeps transmitting at that position.
%This means that no other neighbor in the two-hop neighborhood has picked the same color.
%In this case, the station will defer the transmission of the next beacon a deterministic number of spots equal to the schedule length $S$.

%If a node in the two-node neighborhood pick the same color, the node that is a common neighbor of both will not receive the beacon and therefore will not confirm the correct reception.
%In this case, the station will defer the transmission of the next beacon a random number of spots.
%A sensible choice is to use an uniform variable between 1 and $2S$ so that the expectation of the random variable roughly coincides with the deterministic backoff used by successful stations.
